Halo alignments with large scale tidal and velocity fields

### 2013-03-03 paper/main.tex
New Mass Relation Plots

\title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Sergio Contreras$^{1}$ 
  Jaime E. Forero-Romero$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

@@

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}

>>>>

\title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Sergio Contreras$^{1}$ 
  Jaime E. Forero-Romero$^{1}$ 
  Nelson Padilla$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/Web.ps}
\caption{Median of the interweb alignment for the two grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/VWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/TWeb.ps}
\caption{Median of the shape alignment for the two web  and the two grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}
\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jVWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jTWeb.ps}
\caption{Median of the angular momentum for the two web  and the two grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}
\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
\end{figure*}
